Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-19 article.tex
fix notation
typo

% Datasets
To assess our method, we have used four datasets provided by the organizers
of the Connectomics challenge : \textit{normal-1, normal-2, normal-3, normal-4}.
Those datasets have $|V|=1000$ time series of length $T=179500$ of image
calcium from simulated neuronal networks \citep{stetter2012model}. Those
networks have approximately 15000 edges.

@@

\item \textbf{GENIE3} \citep{huynhthu2010inferring} translates the inference of the
network of $p$ neurons into $p$ supervised learning tasks. For each task,
the fluorescence of a neuron is predicted from the fluorescence
of all other neurons using a tree based ensemble such as
random forest \citep{breiman2001random}. The tree ensemble associate a
variable importance scores \citep{louppe2013understanding}
to each neuron used in the predictions, which is used as a connectivity
score. The following parameters are used
$10000$ trees, $\log_2{p}$ variables are randomly selected to split a tree
node and the maximal tree depth is constrained to 1, 2 or 3.
\end{itemize}

>>>>

% Datasets
To assess our method, we have used four datasets provided by the organizers
of the Connectomics challenge : \textit{normal-1, normal-2, normal-3, normal-4}.
Those datasets have $p=1000$ time series of length $T=179500$ of image
calcium from simulated neuronal networks \citep{stetter2012model}. Those
networks have approximately 15000 edges.

@@

\item \textbf{GENIE3} \citep{huynhthu2010inferring} translates the inference of the
network of $p$ neurons into $p$ supervised learning tasks. For each task,
the fluorescence of a neuron is predicted from the fluorescence
of all other neurons using a tree based ensemble such as
random forest \citep{breiman2001random}. The tree ensemble associate a
variable importance scores \citep{louppe2013understanding}
to each neuron used in the predictions, which is used as a connectivity
score. The following parameters are used
$10000$ trees, $\log_2{p}$ variables are randomly selected to split tree
nodes and the maximal tree depth is constrained to 1, 2 or 3.
\end{itemize}
